Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-25 sattose/paper.tex
Made it more verbose
Because this makes it clearer what exactly I mean with stuff

Because of that, for this research we have looked into a redefinition of type 2 clones to be able to detect such clones that can and should be merged. Our definition ensures functional similarity by considering types, having a distinction between different variables and defining thresholds for variability in literals.

>>>>

Because of that, for this research we have looked into a redefinition of type 2 clones to be able to detect such clones that can and should be merged. Our definition ensures functional similarity by applying the following changes to type 2 clones:

\begin{itemize}
  \item \textbf{Considering types:} The definition of type 2 clones defines that types should not be considered. We disagree, because types can make a significant change to the meaning of a code segment and thus whether this segment should be considered a clone. For instance, we should not say that an Apple type object is the same as an object of Orange type (don't compare apples with oranges).
  \item \textbf{Having a distinction between different variables:} By the definition of type 2 clones any identifiers would not be taken into account. We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables. For instance, if we call a method like this: \textit{``myMethod(var1, var2)''}, or call this method like this: \textit{``myMethod(var1, var1)''}. Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
  \item \textbf{Defining a threshold for variability in literals:} By the definition of type 2 clones any literals would not be taken into account. We agree, as when merging the clone (for instance by extracting a method), we can simply turn the literal into a method parameter. However, we would argue that thresholds matter here. How many literals may differ for the segment still to be considered a clone with another segment? We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
\end{itemize}
